Enhancing Student Engagement via Reduction of Frustration with Programming Assignments using Machine Learning

### 2017-06-12 paper.tex
Error found

\abstract{Learning to program is often regarded as a difficult task. When
selecting an appropriate programming exercise, experienced instructors
gauge a student\’s affective state and skills to then assign an
activity with the appropriate level of difficulty. This work is
focused on the prediction of the affective states of programmers with
different levels of expertise when learning a new programming
language. For this, an interactive web-based programming platform is
proposed. The platform is designed to collect data from the students\'
interaction for data analysis. Current work is focused on the
prediction of affective states using non-obtrusive
sensors. Specifically, the aim of this research is to evaluate the use
of keyboard and mouse dynamics as an appropriate sensory input for an
affective recognition system. The proposed method uses feature vectors
obtained by mining data generated from both keyboard and mouse
dynamics of students as they work in basic Python programming
assignments, which were used to train different classification
algorithms to classify learners into five different affective states:
boredom, frustration, distraction, relaxation and engagement. Accuracy
achieved was around 75\% with J48 obtaining the best results, proving
that data gathered from non-obtrusive sensors can successfully be used
as another input to classification models in order to predict an
individual\'s affective states.}

>>>>

\abstract{Learning to program is often regarded as a difficult task. When
selecting an appropriate programming exercise, experienced instructors
gauge a student\'s affective state and skills to then assign an
activity with the appropriate level of difficulty. This work is
focused on the prediction of the affective states of programmers with
different levels of expertise when learning a new programming
language. For this, an interactive web-based programming platform is
proposed. The platform is designed to collect data from the students\'
interaction for data analysis. Current work is focused on the
prediction of affective states using non-obtrusive
sensors. Specifically, the aim of this research is to evaluate the use
of keyboard and mouse dynamics as an appropriate sensory input for an
affective recognition system. The proposed method uses feature vectors
obtained by mining data generated from both keyboard and mouse
dynamics of students as they work in basic Python programming
assignments, which were used to train different classification
algorithms to classify learners into five different affective states:
boredom, frustration, distraction, relaxation and engagement. Accuracy
achieved was around 75\% with J48 obtaining the best results, proving
that data gathered from non-obtrusive sensors can successfully be used
as another input to classification models in order to predict an
individual\'s affective states.}
